Draft 1

### 2012-05-09 Thesis - Presentation/draft1.tex
Wed MAY 9th 2012 23:08

\documentclass[a4paper,10pt]{report}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
%\usepackage{abssymb}
%opening
\title{Thesis Draft 1}
\author{Anupam Prasad Vedurmudi}

@@

\subsection{Python Implementation}
\section{FEM Formulation of Quantum Mechanics}
The Schrödinger equation for a wave function $\psi$ is given by,

@@

\section{Toy Problem - Scattering in 1D}
We now use the above methods in an example with scattering off a potential in 1D. Due to the simplicity of the problem,
it is possible to explicitly calculate the exact Green's function by inverting the appropriate matrix according the formal
definition given in \eqref{GFdefinition}. We will examine the problem in two cases: 
\begin{itemize}
 \item In the first case, we have convergence with both the modified and unmodified Hamiltonian but at a faster rate with the modification.
 \item In the second case, the modified hamiltonian gives a convergent Born series whereas the unmodified one diverges. 
\end{itemize}

@@

We see that the Born Series converges to the exact value in both cases but that the modified case converges in fewer iterations.

\subsection{Second Case}
In the second case, we define the potential as, 
\begin{equation}\label{potentialdef2}
V = -200\mathtt{exp}(-(x-3.5)^2/0.5)-200\mathtt{exp}(-(x-6.5)^2/0.5)
\end{equation}

@@

We see that the Born Series in the modified case converges to the exact value but diverges in the original case.

\bibliographystyle{plain}
\bibliography{draft1.bib}
\end{document}

>>>>

\documentclass[a4paper,10pt]{report}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
%\usepackage{abssymb}
%opening
\title{Draft 1}
\author{Anupam Prasad Vedurmudi}

@@

\subsection{Python Implementation}
\section{FEM in Quantum Mechanics}
The Schrödinger equation for a wave function $\psi$ is given by,

@@

\section{Toy Problem - Scattering in 1D}
We now use the above methods in an example with scattering off a potential in 1D. Due to the simplicity of the problem,
it is possible to explicitly calculate the exact Green's function by inverting the appropriate matrix according the formal
definition given in \eqref{GFdefinition}. We will examine the problem in three cases: 
\begin{itemize}
 \item In the first case, we have convergence with both the modified and unmodified Hamiltonian but at a faster rate with the modification.
 \item In the second case, the unmodified case converges for certain energies and diverges for others.With the modification, we always have
       faster convergence.
 \item In the third case, the modified hamiltonian gives a convergent Born series whereas the unmodified one diverges. 
\end{itemize}

@@

We now plot the elements of the Born Series against the number of iterations. In order
to compare the modified and unmodified cases, we plot them side by side with the modified case on the left and the unmodified one
on the right. We follow this convention in the other two cases as well.

\begin{center}
\begin{figure}[lht]
\includegraphics[width=360pt, height=200pt]{series1a.png}
%\caption[\textwidth]{First Case}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[lht]
\includegraphics[width=360pt, height=200pt]{series1b.png}
%\caption[\textwidth]{First Case}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[lht]
\includegraphics[width=360pt, height=200pt]{series1c.png}
%\caption[\textwidth]{First Case}
\end{figure}
\end{center}

We see that the Born Series converges to the exact value in both cases. It is also to be noted that the 
.

\subsection{Second Case}
In the second case, we define the potential as, 
\begin{equation}\label{potentialdef2}
V = \begin{cases}
-0.5 &\mbox{} 4\leq x\leq 6\\
0 &\mbox{ otherwise}
\end{cases} 
\end{equation}

@@

\begin{center}
\begin{figure}[lht]
\includegraphics[width=360pt, height=200pt]{series2a.png}
%\caption[\textwidth]{First Case}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[lht]
\includegraphics[width=360pt, height=200pt]{series2b.png}
%\caption[\textwidth]{First Case}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[lht]
\includegraphics[width=360pt, height=200pt]{series2c.png}
%\caption[\textwidth]{First Case}
\end{figure}
\end{center}

We see that for the original Hamiltonian, the Born series converges in some cases but doesn't in others. However,
with the modification, we always have convergence at a faster rate.
\subsection{Third Case}
\begin{equation}\label{potentialdef2}
V = -200\mathtt{exp}(-(x-3.5)^2/0.5)-200\mathtt{exp}(-(x-6.5)^2/0.5)
\end{equation}

\begin{center}
\begin{figure}[lht]
\includegraphics[width=360pt, height=200pt]{series3a.png}
%\caption[\textwidth]{First Case}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[lht]
\includegraphics[width=360pt, height=200pt]{series3b.png}
%\caption[\textwidth]{First Case}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[lht]
\includegraphics[width=360pt, height=200pt]{series3c.png}
%\caption[\textwidth]{First Case}
\end{figure}
\end{center}

We see that the Born Series in the modified case converges to the exact value but diverges in the original case.
\bibliographystyle{plain}
\bibliography{draft1.bib}
\end{document}
